% NeurIPS 2026 submission skeleton.  Content lives primarily in paper/sections/*.md;
% this file is the LaTeX consolidation.  Compiled form is produced via pandoc
% or by pasting the sections into the neurips_2026 style file.
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm, mathtools, bm}
\usepackage{booktabs, array}
\usepackage{hyperref}
\usepackage{graphicx}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{assumption}{Assumption}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Var}{Var}
\newcommand{\ind}{\mathbb{1}}
\newcommand{\indep}{\perp\!\!\!\perp}

\title{RuleOPE: Doubly-Robust Offline Evaluation of Compositional Rule-Based
Interventions in Retrieval-Augmented Generation}

\author{Anonymous submission}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Production retrieval-augmented generation (RAG) systems are routinely updated
by the addition of deterministic \emph{rules} that filter, re-rank, or veto the
retrieval step based on boolean predicates over query and passage features.
There is, however, no principled way to decide \emph{which} rule to ship.
Existing off-policy evaluation estimators are specialised to stochastic or
continuous-action bandits, or treat retrieval as a slate recommender, ignoring
the combinatorial structure of rules.  We introduce RuleOPE, an offline
evaluation framework for rule-based interventions in RAG.  Our contributions
are: (i) a formalisation of rule-based interventions as conjunctive boolean
policies; (ii) a doubly-robust estimator whose reward regression is
factorised over atomic predicates, so rules sharing atoms share regression
parameters and the total estimator variance across a rule set of size $M$
scales sublinearly in $M$; and (iii) a consistency proof and variance bound
under standard ignorability assumptions, plus explicit characterisation of
three RAG-specific failure modes.  We release a frozen benchmark of 500
rules with exact ground-truth values, three correction-noise regimes, and a
reproducible synthetic substrate.  RuleOPE matches or improves upon every
baseline including Cascade DR, CIPS-DR, and the Direct Method, with the
largest gains in the production-realistic deterministic-logging regime.
\end{abstract}

%-----------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}
\input{sections/intro_body}

%-----------------------------------------------------------------------------
\section{Related work}
\label{sec:related}
\input{sections/related_body}

%-----------------------------------------------------------------------------
\section{Problem formulation}
\label{sec:formulation}
\input{sections/formulation_body}

%-----------------------------------------------------------------------------
\section{The RuleOPE estimator}
\label{sec:estimator}
\input{sections/estimator_body}

%-----------------------------------------------------------------------------
\section{Theory}
\label{sec:theory}
\input{sections/theory_body}

%-----------------------------------------------------------------------------
\section{Benchmark}
\label{sec:benchmark}
\input{sections/benchmark_body}

%-----------------------------------------------------------------------------
\section{Main experiments}
\label{sec:exp}
\input{sections/experiments_body}

%-----------------------------------------------------------------------------
\section{Ablations and scaling}
\label{sec:abl}
\input{sections/ablations_body}

%-----------------------------------------------------------------------------
\section{Failure-mode stress tests and case study}
\label{sec:failure}
\input{sections/failure_body}

%-----------------------------------------------------------------------------
\section{Discussion}
\label{sec:disc}
\input{sections/discussion_body}

%-----------------------------------------------------------------------------
\appendix
\section{Consistency proof (detailed)}
See \texttt{theory/proofs.tex}.

\section{Decisions log}
\input{sections/decisions_body}

%-----------------------------------------------------------------------------
\section*{References}
\small
\begin{itemize}\itemsep=1pt
\item Chernozhukov et al.\ (2018).  Double/debiased machine learning.  \emph{Econometrics Journal}.
\item Dud\'ik, Langford, Li (2011).  Doubly robust policy evaluation and learning.  \emph{ICML}.
\item Es et al.\ (2023).  RAGAS: automated evaluation of RAG.  \emph{arXiv}.
\item Farajtabar et al.\ (2018).  More robust doubly robust OPE.  \emph{ICML}.
\item Horvitz, Thompson (1952).  A generalization of sampling without replacement.  \emph{JASA}.
\item Joachims et al.\ (2018).  Deep learning with logged bandit feedback.  \emph{ICLR}.
\item Kallus, Uehara (2020).  Double reinforcement learning.  \emph{JMLR}.
\item Kiyohara et al.\ (2022).  Doubly robust off-policy evaluation for ranking.  \emph{WSDM}.
\item Li et al.\ (2015).  Counterfactual estimation for slate recommender systems.  \emph{RecSys}.
\item McInerney et al.\ (2020).  Counterfactual evaluation of slate recommendations.  \emph{RecSys}.
\item Petroni et al.\ (2021).  KILT: a benchmark for knowledge-intensive tasks.  \emph{NAACL}.
\item Robins, Rotnitzky, Zhao (1994).  Estimation of regression coefficients when some regressors are not always observed.  \emph{JASA}.
\item Rosenbaum, Rubin (1983).  The central role of the propensity score.  \emph{Biometrika}.
\item Rubin (1974).  Estimating causal effects of treatments.  \emph{J.\ Ed.\ Psych.}
\item Saad-Falcon et al.\ (2023).  ARES: evaluation of RAG.  \emph{NAACL}.
\item Saito, Joachims (2022).  Off-policy evaluation for large action spaces.  \emph{ICML}.
\item Saito et al.\ (2023).  OPE for deterministic policies with kernel smoothing.  \emph{arXiv}.
\item Shivaswamy, Joachims (2015).  Coactive learning.  \emph{JMLR}.
\item Su et al.\ (2020).  Doubly robust off-policy evaluation with shrinkage.  \emph{ICML}.
\item Swaminathan, Joachims (2015).  Counterfactual risk minimization.  \emph{JMLR}; The self-normalized estimator, \emph{NeurIPS}.
\item Swaminathan et al.\ (2017).  Off-policy evaluation for slate recommendation.  \emph{NeurIPS}.
\item Thakur et al.\ (2021).  BEIR: a heterogenous benchmark for zero-shot evaluation of IR.  \emph{NeurIPS}.
\item Vlassis et al.\ (2019).  OPE for combinatorial actions.  \emph{ICML workshop}.
\item Wang et al.\ (2017).  Optimal and adaptive off-policy evaluation in contextual bandits.  \emph{ICML}.
\item Yang et al.\ (2018).  HotpotQA: a diverse multi-hop QA dataset.  \emph{EMNLP}.
\item Zhang et al.\ (2020).  Off-policy evaluation with sparse expert feedback.  \emph{AISTATS}.
\end{itemize}

\end{document}
